R script for:
MA on the effects of maternal nutrition on offsprong's coping styles

STEP 1: data upload, cleaning and reshaping (preprocessing script) 

(based on code bits originally written by Alistair, modified by Losia)

========================================================

1. data upload  
--------------
```{r load, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
rm(list=ls())
getRversion()
options(scipen=100)

#install.packages("car")
library(car)

data <- read.csv("data/main_data_processed.csv") #start from data processed for Hedges d analyses
names(data)
dim(data) #390 84
#str(data)
```

2.  calculate lnRR and its variance as alternative effect size measure
------------------------------------------
```{r calc lnRR, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
## Calculate lnRR (based on Alistair's code)
#Calc.lnRR<-function(CMean, EMean){
#lnRR<-log(EMean / CMean)
#return(lnRR)
#}
#Calc.var.lnRR<-function(CMean, CN, CSD, EMean, EN, ESD){
#EVar<-ESD^2
#CVar<-CSD^2
#V <- (CVar / (CN * (CMean^2))) + (EVar / (EN * (EMean^2))) #diagonal
#return(V)
#}

data$lnRR <- log(data$exp_mean / data$con_mean)
range(data$lnRR) #Inf value due to some means being 0 - find and replace 0 with 0.01
data[data$lnRR==Inf, ] # comp_183
data[data$con_mean==0, "con_mean"] <- 0.01 #fix the problem
data$lnRR <- log(data$exp_mean / data$con_mean) #recalculate after removing 0 mean
range(data$lnRR) #ok

data$lnRR_Var <- (data$varianceofcontrols / (data$con_n * (data$con_mean^2))) + (data$varianceoftreatment / (data$exp_n * (data$exp_mean^2))) #use for the var-covar matrix diagonal
data$lnRR_SE <- sqrt(data$lnRR_Var)

#controlling lnRR variance for shared control group among some treatment groups 
#data$lnRR_Var_adj <- (CVar / (CN * (CMean^2))) #adjusted variance for cases with shared contol group - use in the var-covar matrix
```

Special case with comp613 - means represent percentages, take out this data point (we cannot use it with lnRR)
------------------------------------------
```{r remove comp_613, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
data <- data[which(data$comp_ID != "comp_613"),]
```

3.  tidy-up outcome directions for lnRR - reversing the signs for some RR values
---------------------------------------------------------
FOR SOME ANXIETY BASED MEASURES A HIGHER VALUE AMONGST THE TREATMENT GROUP ACTUALLY EQUATES TO A DECREASE IN ANXIETY THERE VALUES NEED TO BE INVERTED (get opposite sign)

```{r outcome signs lnRR, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
data$lnRR[which(data$high_better == "yes" & data$my.behaviour == "ANXIETY")] <- data$lnRR[which(data$high_better == "yes" & data$my.behaviour == "ANXIETY")] * -1
data$lnRR[which(data$high_better == "no" & data$my.behaviour == "EXPLORATION")] <- data$lnRR[which(data$high_better == "no" & data$my.behaviour == "EXPLORATION")] * -1
data$lnRR[which(data$high_better == "no" & data$my.behaviour == "ACTIVITY")] <- data$lnRR[which(data$high_better == "no" & data$my.behaviour == "ACTIVITY")] * -1
```

4. save the main data and data subsets
--------------------------------------------------------------
```{r save and split data, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}

# save the main processed data file
write.table(data, file="data/main_data_processed_lnRR.csv", sep=",", col.names=names(data), row.names=F)

# split the main processed data by treatment and outcomes and save into a separate files
cal.plus.data <- data[which(data$treatment=="calorie+"),]
cal.neg.data <- data[which(data$treatment=="calorie-"),]
pro.neg.data <- data[which(data$treatment=="protein-"),]

write.table(cal.plus.data[which(cal.plus.data$my.behaviour == "ACTIVITY"),], file="data/Cal.Plus.Act_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(cal.neg.data[which(cal.neg.data$my.behaviour == "ACTIVITY"),], file="data/Cal.Neg.Act_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(pro.neg.data[which(pro.neg.data$my.behaviour == "ACTIVITY"),], file="data/Pro.Neg.Act_lnRR.csv", sep=",", col.names=names(data), row.names=F)

write.table(cal.plus.data[which(cal.plus.data$my.behaviour == "EXPLORATION"),], file="data/Cal.Plus.Exp_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(cal.neg.data[which(cal.neg.data$my.behaviour == "EXPLORATION"),], file="data/Cal.Neg.Exp_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(pro.neg.data[which(pro.neg.data$my.behaviour == "EXPLORATION"),], file="data/Pro.Neg.Exp_lnRR.csv", sep=",", col.names=names(data), row.names=F)

write.table(cal.plus.data[which(cal.plus.data$my.behaviour == "ANXIETY"),], file="data/Cal.Plus.Anx_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(cal.neg.data[which(cal.neg.data$my.behaviour == "ANXIETY"),], file="data/Cal.Neg.Anx_lnRR.csv", sep=",", col.names=names(data), row.names=F)
write.table(pro.neg.data[which(pro.neg.data$my.behaviour == "ANXIETY"),], file="data/Pro.Neg.Anx_lnRR.csv", sep=",", col.names=names(data), row.names=F)
```

5. create and save data as a list
--------------------------------------------------------------
```{r save data list, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
#data <- read.csv("data/main_data_processed_lnRR.csv")

#main_data <- data

#Overfeeding
data1 <- read.csv("data/Cal.Plus.Act_lnRR.csv")
data2 <- read.csv("data/Cal.Plus.Exp_lnRR.csv")
data3 <- read.csv("data/Cal.Plus.Anx_lnRR.csv")
#Caloric restriction
data4 <- read.csv("data/Cal.Neg.Act_lnRR.csv")
data5 <- read.csv("data/Cal.Neg.Exp_lnRR.csv")
data6 <- read.csv("data/Cal.Neg.Anx_lnRR.csv")
#Protein restriction
data7 <- read.csv("data/Pro.Neg.Act_lnRR.csv")
data8 <- read.csv("data/Pro.Neg.Exp_lnRR.csv")
data9 <- read.csv("data/Pro.Neg.Anx_lnRR.csv")

#put all subsets in a list:
data_list <- list(data1=data1,data2=data2,data3=data3,data4=data4,data5=data5,data6=data6,data7=data7,data8=data8,data9=data9)
#str(data_list[[1]])
#names(data_list[[1]])

```

12. scale continous predictors
---------------------------------------------------------------------------------------------------
```{r scaling, echo=FALSE, message=FALSE, eval=TRUE, include=FALSE}
#scaling continuous moderators: nom_manip_val, dam_diet_start_dPC, dam_diet_end_dPC, response_age_dPP
Z_data_list <- lapply(data_list, function(x) {
  Z_nom_manip_val <- scale(x$nom_manip_val)
  Z_nom_manip_val2 <- scale(x$nom_manip_val2)
  Z_dam_diet_start_dPC <- scale(x$dam_diet_start_dPC)
  Z_dam_diet_end_dPC <- scale(x$dam_diet_end_dPC)
  Z_response_age_dPP <- scale(x$response_age_dPP)
  Z_delay <- scale(x$response_age_dPP-x$dam_diet_end_dPC)
  cbind(x,Z_nom_manip_val,Z_dam_diet_start_dPC,Z_dam_diet_end_dPC,Z_response_age_dPP,Z_delay)
  })
names(Z_data_list[[1]]) #check column names

save(Z_data_list,file="data/Z_data_list_lnRR.Rdata")
#rm(Z_data_list)
```

*************************************
Check correlations among N SD and Hd
------------------------------------
```{r corr N SD Hd, echo=TRUE, message=FALSE, eval=TRUE, include=FALSE}
library(psych)
library(Matrix)

#load("data/Z_data_list_lnRR.Rdata") ####upload data in a list format: for the 9 subsets

#Z_data_list[[2]] <- NULL #exclude subset data2 from the data list - carefull the indexes will shuffle by 1!!!
#df <- Z_data_list[[1]]

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[1]])
#cor.test(Z_data_list[[1]]$H.d, Z_data_list[[1]]$exp_n)
pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[3]])

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[4]])

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[5]])

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[6]])

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[7]])

pairs.panels(~H.d + H.d_Var_combined + exp_n + con_n + lnRR + lnRR_Var, main="Cal.Plus.Act (n=33)", lm=TRUE, ellipses=FALSE, jiggle=TRUE, data=Z_data_list[[8]])

```
