R script for:
MA on the effects of maternal nutrition on offsprong's coping styles

STEP 7: preparing plots for the MS
============================================================
  
1. Start  
--------------

```{r start, echo=FALSE, message=FALSE}
rm(list=ls())
#getRversion()
options(scipen=100)

library(MCMCglmm)
library(meta)

load("data/Z_data_list.Rdata") ####upload data in a list format: for the 9 subsets

#Z_data_list[[2]] <- NULL #exclude subset data2 from the data list - carefull, the indexes will shuffle by 1!!!

```


2. forest plots - rearranged 
--------------------------------------------------------------------------------
Zero effect size is shown as dashed line.
Statistically significant effects marked by star.

```{r forest plot}
varnames_full <- rev(c("Male mean","Mixed-sex mean", "Female mean","Dam dietary manipulation level",
                "Dam dietary manipulation start time","Offspring age at testing","Dam dietary manipulation end time","Meta-analytic (overall) mean"))
varnames_models <- rev(c("factor(sex)m","factor(sex)both","factor(sex)f","Z_nom_manip_val","Z_dam_diet_start_dPC","Z_response_age_dPP","Z_dam_diet_end_dPC","intercept"))
varnames <- as.data.frame(cbind(varnames_models, varnames_full))

#tiff(file="plots/Rplot_forest_plot_v2.tif",width=6.30708661,height=4,res=400,units="in",pointsize=9)
pdf(file="plots/Rplot_forest_plot_v2.pdf",width=16,height=8,pointsize=14,family="sans",encoding="CP1250")

par(mfcol=c(3,3),mar=c(4,14,2,1),oma=c(0,1,0,0))


###### Cal.Neg.Act (sub3)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 5) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "a) Caloric restriction - Activity", adj = 0, cex=1.2)

stars<-c("*","","","","","","","")
for (i in 1:length(stars)){
  #mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1) #for placing stars on the outer margin
  text(x = 1, y = i, labels = stars[i], las=2, cex=2)
}


###### Cal.Neg.Exp (sub4)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegExp_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegExp_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "d) Caloric restriction - Exploration", adj = 0, cex=1.2)

stars<-c("","","","","*","","","")
for (i in 1:length(stars)){
  #mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1)
  text(x = 1, y = i, labels = stars[i], las=2, cex=2)
}


###### Cal.Neg.Anx (sub5)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 4) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "g) Caloric restriction - Anxiety", adj = 0, cex=1.2)


###### Pro.Neg.Act (sub6)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
#add labels
#for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "b) Protein restriction - Activity", adj = 0, cex=1.2)


###### Pro.Neg.Exp (sub7)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegExp_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegExp_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
#add labels
#for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "e) Protein restriction - Exploration", adj = 0, cex=1.2)


###### Pro.Neg.Anx (sub8)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
#for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "h) Protein restriction - Anxiety", adj = 0, cex=1.2)

stars<-c("","","","","","","","*")
for (i in 1:length(stars)){
  #mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1)
  text(x = 1, y = i, labels = stars[i], las=2, cex=2)
  }


###### Cal.Plus.Act (sub1)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalPlusAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 3) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalPlusAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
#add labels
#for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "c) Obesogenic - Activity", adj = 0, cex=1.2)


###### Cal.Plus.Anx (moment method - only overall result available)
data <- read.csv("data/Cal.Plus.Exp.csv")
weights <- 1/data$SE.d^2
effects <- data$H.d
mu <- sum(effects * weights) / sum(weights)
var <- 1 / sum(weights)
t <- mu / sqrt(var)
CI <- sqrt(var) * qt(0.05/2, df=1)
#mu+CI # -3.619431
#mu    #  1.129344
#mu-CI #  5.878119
#plot mean
plot(mu,1,ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="",pch=Shape,cex=Size,cex.axis=.9)
# add segments
segments(mu+CI,1,mu-CI,1,lwd=1.25)
#add labels
#for (i in 1:length(varnames$varnames_full)){   mtext(varnames$varnames_full[i],2,0,at=i,las=2,cex=.7) }
abline(v=0,lty=3)
title(main = "f) Obesogenic - Exploration", adj = 0, cex=1.2)


###### Cal.Plus.Anx (sub2)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalPlusAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 5) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalPlusAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
#for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "i) Obesogenic - Anxiety", adj = 0, cex=1.2)

dev.off()


### Edit the gaps between plots in Adobe Illustrator! (change Myriad font to Zapf Dingbat!)
```

3. funnel plots on raw data  - rearranged
--------------------------------------------------------------------------------
Raw effect size estimates (difference between prenatally manipulated and control offspring groups; Hedge’s d) plotted against their precision (1/SE)
Overall postrior (meta-analytic) means are shown as solid lines. 
Zero effect size is shown as dashed line.

```{r funnel raw, echo=FALSE, message=FALSE}

pdf(file="plots/Rplot_funnel_raw_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))

###### Cal.Neg.Act (sub3)
df <- Z_data_list[[4]]
meta_sub3 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub3, yaxis = "invse", xlab="", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.705, col="red", lwd=1, lty=1)
title(main = "a) Caloric restriction - Activity", adj=0)

###### Cal.Neg.Exp (sub4)
df <- Z_data_list[[5]]
meta_sub4 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub4, yaxis = "invse", xlab="", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.382, col="red", lwd=1, lty=1)
title(main = "d) Caloric restriction - Exploration", adj=0)

###### Cal.Neg.Anx (sub5)
df <- Z_data_list[[6]]
meta_sub5 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub5, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.338, col="red", lwd=1, lty=1)
title(main = "g) Caloric restriction - Anxiety", adj=0)

###### Pro.Neg.Act (sub6)
df <- Z_data_list[[7]]
meta_sub6 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub6, yaxis = "invse", xlab="", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.067, col="red", lwd=1, lty=1)
title(main = "b) Protein restriction - Activity", adj=0)

###### Pro.Neg.Exp (sub7)
df <- Z_data_list[[8]]
meta_sub7 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub7, yaxis = "invse", xlab="", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.007, col="red", lwd=1, lty=1)
title(main = "e) Protein restriction - Exploration", adj=0)

###### Pro.Neg.Exp (sub8)
df <- Z_data_list[[9]]
meta_sub8 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub8, yaxis = "invse", xlab="Hedge's d", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.074, col="red", lwd=1, lty=1)
title(main = "h) Protein restriction - Anxiety", adj=0)

###### Cal.Plus.Act (sub1)
df <- Z_data_list[[1]]
meta_sub1 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub1, yaxis = "invse", xlab="", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.238, col="red", lwd=1, lty=1)
title(main = "c) Obesogenic - Activity", adj=0)

###### Cal.Plus.Exp
df <- Z_data_list[[2]]
meta_sub2 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub2, yaxis = "invse", xlab="", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2)
abline(v=0, lwd=1, lty=2)
abline(v=1.129, col="red", lwd=1, lty=1)
title(main = "f) Obesogenic - Exploration", adj=0)

###### Cal.Plus.Anx (sub2)
df <- Z_data_list[[3]]
meta_sub2 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub2, yaxis = "invse", xlab="Hedge's d", ylab="", xlim=c(-5,5), ylim=c(0,6), pch=1, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.173, col="red", lwd=1, lty=1)
title(main = "i) Obesogenic - Anxiety", adj=0)

dev.off()
```

4. funnel plots on residuals from full models - rearranged
--------------------------------------------------------------------------------
Residual effect sizes from the full model (adjusted for moderators) plotted against their precision (1/SE)
Zero effect size is shown as dashed line.

```{r funnel res, echo=FALSE, message=FALSE}
pdf(file="plots/Rplot_funnel_residuals_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))

###### Cal.Neg.Act (sub3)
df <- Z_data_list[[4]]
load("runs/M3.3_sub3.Rdata") #load best full model results
model_sub3 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub3 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub3 <- df$H.d - predict(model_sub3)
zes_sub3 <- es_sub3*prec_sub3
plot(es_sub3,prec_sub3, xlab="", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "a) Caloric restriction - Activity", adj=0)

###### Cal.Neg.Exp (sub4)
df <- Z_data_list[[5]]
load("runs/M3.3_sub4.Rdata") #load best full model results
model_sub4 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub4 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub4 <- df$H.d - predict(model_sub4)
zes_sub4 <- es_sub4*prec_sub4
plot(es_sub4,prec_sub4, xlab="", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "d) Caloric restriction - Exploration", adj=0)

###### Cal.Neg.Anx (sub5)
df <- Z_data_list[[6]]
load("runs/M3.3_sub5.Rdata") #load best full model results
model_sub5 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub5 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub5 <- df$H.d - predict(model_sub5)
zes_sub5 <- es_sub5*prec_sub5
plot(es_sub5,prec_sub5, xlab="Hedges's d (residuals)", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "g) Caloric restriction - Anxiety", adj=0)

###### Pro.Neg.Act (sub6)
df <- Z_data_list[[7]]
load("runs/M3.2_sub6.Rdata") #load best full model results
model_sub6 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub6 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub6 <- df$H.d - predict(model_sub6)
zes_sub6 <- es_sub6*prec_sub6
plot(es_sub6,prec_sub6, xlab="", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "b) Protein restriction - Activity", adj=0)

###### Pro.Neg.Exp (sub7)
df <- Z_data_list[[8]]
load("runs/M3.2_sub7.Rdata") #load best full model results
model_sub7 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub7 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub7 <- df$H.d - predict(model_sub7)
zes_sub7 <- es_sub7*prec_sub7
plot(es_sub7,prec_sub7, xlab="", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "e) Protein restriction - Exploration", adj=0)

###### Pro.Neg.Anx (sub8)
df <- Z_data_list[[9]]
load("runs/M3.2_sub8.Rdata") #load best full model results
model_sub8 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub8 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub8 <- df$H.d - predict(model_sub8)
zes_sub8 <- es_sub8*prec_sub8
plot(es_sub8,prec_sub8, xlab="Hedges's d (residuals)", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "h) Protein restriction - Anxiety", adj=0)

###### Cal.Plus.Act (sub1)
df <- Z_data_list[[1]]
load("runs/M3.1_sub1.Rdata") #load best full model results
model_sub1 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub1 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub1 <- df$H.d - predict(model_sub1)
zes_sub1 <- es_sub1*prec_sub1
plot(es_sub1,prec_sub1, xlab="", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "c) Obesogenic - Activity", adj=0)

###### Cal.Plus.Exp (moments method! use (x - mu) as residuals)
df <- Z_data_list[[2]]
prec_moment <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_moment <- df$H.d - 1.129344
zes_moment <- es_moment*prec_moment
plot(es_moment, prec_moment, xlab="", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "f) Obesogenic - Exploration", adj=0)

###### Cal.Plus.Anx (sub2)
df <- Z_data_list[[3]]
load("runs/M3.1_sub2.Rdata") #load best full model results
model_sub2 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub2 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub2 <- df$H.d - predict(model_sub2)
zes_sub2 <- es_sub2*prec_sub2
plot(es_sub2,prec_sub2, xlab="Hedges's d (residuals)", ylab="", xlim=c(-5,5), ylim=c(0,8), pch=1, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "i) Obesogenic - Anxiety", adj=0)

dev.off()
```

5. Plot of distributions of continous predictors as histograms and as lines - rearranged
----------------------------------------------------------------------------------------
```{r plot cont distr, echo=FALSE, message=FALSE}

### nominal manipulation value

pdf(file="plots/Rplot_hist_nom_manip_val_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))
data <- Z_data_list[[4]]
hist(data$nom_manip_val, xlim=c(30,80),ylim=c(0,80),main="",xlab="",ylab="Frequency [%]")
title(main="a) Caloric restriction - Activity", adj=0)
data <- Z_data_list[[5]]
hist(data$nom_manip_val, main="",xlim=c(30,80),ylim=c(0,80),xlab="",ylab="Frequency [%]")
title(main="d) Caloric restriction - Exploration", adj=0)
data <- Z_data_list[[6]]
hist(data$nom_manip_val, main="",xlim=c(30,80),ylim=c(0,80),xlab="Dam dietary manipulation level [% control]",ylab="")
title(main="g) Caloric restriction - Anxiety", adj=0)
data <- Z_data_list[[7]]
hist(data$nom_manip_val, main="",xlim=c(0,60),ylim=c(0,80),xlab="",ylab="")
title(main="b) Protein restriction - Activity", adj=0)
data <- Z_data_list[[8]]
hist(data$nom_manip_val, main="",xlim=c(0,60),ylim=c(0,80),xlab="",ylab="")
title(main="e) Protein restriction - Exploration", adj=0)
data <- Z_data_list[[9]]
hist(data$nom_manip_val, main="",xlim=c(0,60),ylim=c(0,80),xlab="Dam dietary manipulation level [% control]",ylab="")
title(main="h) Protein restriction - Anxiety", adj=0)
data <- Z_data_list[[1]]
hist(data$nom_manip_val, main="",xlim=c(0,10),ylim=c(0,80),xlab="",ylab="")
title(main="c) Obesogenic - Activity", adj=0)
data <- Z_data_list[[2]]
hist(data$nom_manip_val, main="",xlim=c(0,10),ylim=c(0,80),xlab="",ylab="")
title(main="f) Obesogenic - Exploration", adj=0)
data <- Z_data_list[[3]]
hist(data$nom_manip_val, main="",xlim=c(0,10),ylim=c(0,80),xlab="Dam dietary manipulation level [% control]",ylab="")
title(main="i) Obesogenic - Anxiety", adj=0)

dev.off()


### offspring response age

pdf(file="plots/Rplot_hist_offspr_age_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))
data <- Z_data_list[[4]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="Frequency [%]",breaks=c(22*0:22))
title(main="a) Caloric restriction - Activity", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[5]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="Frequency [%]",breaks=c(22*0:22))
title(main="d) Caloric restriction - Exploration", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[6]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="Offspring age at measurement [days]",ylab="Frequency [%]",breaks=c(22*0:22))
title(main="g) Caloric restriction - Anxiety", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[7]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="",breaks=c(22*0:22))
title(main="b) Protein restriction - Activity", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[8]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="",breaks=c(22*0:22))
title(main="e) Protein restriction - Exploration", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[9]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="Offspring age at measurement [days]",ylab="",breaks=c(22*0:22))
title(main="h) Protein restriction - Anxiety", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[1]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="",breaks=c(22*0:22))
title(main="c) Obesogenic - Activity", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[2]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="",ylab="",breaks=c(22*0:22))
title(main="f) Obesogenic - Exploration", adj=0)
abline(v=22, lty=3)
data <- Z_data_list[[3]]
hist(data$response_age_dPP, main="",xlim=c(0,500),ylim=c(0,80),xlab="Offspring age at measurement [days]",ylab="",breaks=c(22*0:22))
title(main="i) Obesogenic - Anxiety", adj=0)
abline(v=22, lty=3)

dev.off()


### line plot for the start, end and duration of the maternal treatment - ordered version

pdf(file="plots/Rplot_timing_lines_ordered_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))
data <- Z_data_list[[4]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="a) Caloric restriction - Activity", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[5]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="d) Caloric restriction - Exploration", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[6]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="time [days]", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="g) Caloric restriction - Anxiety", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[7]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="b) Protein restriction - Activity", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[8]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="e) Protein restriction - Exploration", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[9]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="time [days]", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="h) Protein restriction - Anxiety", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[1]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="c) Obesogenic - Activity", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[2]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="f) Obesogenic - Exploration", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)
data <- Z_data_list[[3]]
data <- data[order(data$dam_diet_start_dPC,data$dam_diet_end_dPC),]
plot(1, type="n", yaxt="n", xlab="time [days]", ylab="",xlim=c(-100,60),ylim=c(0,110), main="")
title(main="i) Obesogenic - Anxiety", adj=0)
segments(data$dam_diet_start_dPC,1:dim(data)[1],data$dam_diet_end_dPC,1:dim(data)[1])
abline(v=0, lty=3)
abline(v=22, lty=3)
abline(v=43, lty=3)

dev.off()
```

6. Bubble plot of the effects of maternal nutritional manipulation levels on offspring behaviours
-------------------------------------------------------------------------------------------------
```{r plot bubble manip val, echo=FALSE, message=FALSE}
pdf(file="plots/Rplot_bubble_nom_manip_val_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))
data <- Z_data_list[[4]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="Effect size (Hedge's d)",main="",xlim=c(30,75),ylim=c(-5,3))
title(main="a) Caloric restriction - Activity", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[5]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="Effect size (Hedge's d)",main="",xlim=c(30,75),ylim=c(-5,3))
title(main="d) Caloric restriction - Exploration", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[6]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="Dam dietary manipulation level [% control]",ylab="Effect size (Hedge's d)",main="",xlim=c(30,75),ylim=c(-5,3))
title(main="g) Caloric restriction - Anxiety", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[7]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="",main="",xlim=c(0,50),ylim=c(-5,3))
title(main="b) Protein restriction - Activity", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[8]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="",main="",xlim=c(0,50),ylim=c(-5,3))
title(main="e) Protein restriction - Exploration", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[9]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="Dam dietary manipulation level [% control]",ylab="",main="",xlim=c(0,50),ylim=c(-5,3))
title(main="h) Protein restriction - Anxiety", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[1]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="",main="",xlim=c(1,10),ylim=c(-5,3))
title(main="c) Obesogenic - Activity", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[2]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="",ylab="",main="",xlim=c(1,10),ylim=c(-5,3))
title(main="f) Obesogenic - Exploration", adj=0)
#abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)
data <- Z_data_list[[3]]
symbols(data$nom_manip_val,data$H.d, circles=1/data$SE.d,inches=0.1,xlab="Dam dietary manipulation level [% control]",ylab="",main="",xlim=c(1,10),ylim=c(-5,3))
title(main="i) Obesogenic - Anxiety", adj=0)
abline(lm(data$H.d ~ data$nom_manip_val, na.action=na.omit), lwd=2)

dev.off()

```

7. Box-plot of effect sizes by sex
----------------------------------------------------------------------------------------
```{r plot box sex, echo=FALSE, message=FALSE}

### nominal manipulation value

pdf(file="plots/Rplot_boxplot_sex_v2.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,2,1),oma=c(0,1,0,0))
data <- Z_data_list[[4]]
#levels(data$sex)
levels(data$sex) <- c("Both","Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",ylab="Effect size (Hedge's d)",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="a) Caloric restriction - Activity", adj=0)
data <- Z_data_list[[5]]
#levels(data$sex)
levels(data$sex) <- c("Both","Male","Female") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",ylab="Effect size (Hedge's d)",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="d) Caloric restriction - Exploration", adj=0)
data <- Z_data_list[[6]]
#levels(data$sex)
levels(data$sex) <- c("Both","Male","Female") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",ylab="Effect size (Hedge's d)",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="g) Caloric restriction - Anxiety", adj=0)
data <- Z_data_list[[7]]
#levels(data$sex)
levels(data$sex) <- c("Both","Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="b) Protein restriction - Activity", adj=0)
data <- Z_data_list[[8]]
#levels(data$sex)
levels(data$sex) <- c("Both","Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="e) Protein restriction - Exploration", adj=0)
data <- Z_data_list[[9]]
#levels(data$sex)
levels(data$sex) <- c("Both","Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="h) Protein restriction - Anxiety", adj=0)
data <- Z_data_list[[1]]
#levels(data$sex)
levels(data$sex) <- c("Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="c) Obesogenic - Activity", adj=0)
data <- Z_data_list[[2]]
#levels(data$sex)
levels(data$sex) <- c("Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="f) Obesogenic - Exploration", adj=0)
data <- Z_data_list[[3]]
#levels(data$sex)
levels(data$sex) <- c("Female","Male") #rename factor levels
data$sex<-factor(data$sex, levels=c("Male","Female","Both")) #reorder factor levels
boxplot(H.d~sex,data=data,xlab="",main="",ylim=c(-5,3),varwidth=TRUE)
abline(h=0, lwd=0.5)
title(main="i) Obesogenic - Anxiety", adj=0)

dev.off()

```
