R script for:
MA on the effects of maternal nutrition on offsprong's coping styles

STEP 6: forest plots, funnel plots and publication bias test
============================================================
  
1. Start  
--------------

```{r start, echo=FALSE, message=FALSE}
rm(list=ls())
getRversion()
options(scipen=100)

library(MCMCglmm)
library(meta)

load("data/Z_data_list.Rdata") ####upload data in a list format: for the 9 subsets

#Z_data_list[[2]] <- NULL #exclude subset data2 from the data list - carefull, the indexes will shuffle by 1!!!

```

2. PUBLICATION BIAS TESTS (Egger's test) and calculating RESIDUALS for the final funnel plot
--------------------------------------------------------------------------------
Checking the intercepts of Egger’s regressions performed on the model residuals and measurement errors.
Evidence for publication bias if the intercept is significantly different from 0.

```{r bias, echo=FALSE, message=FALSE}

###### Cal.Plus.Act (sub1)
df <- Z_data_list[[1]]
load("runs/M3.1_sub1.Rdata") #load best full model results
model_sub1 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub1 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub1 <- df$H.d - predict(model_sub1)
zes_sub1 <- es_sub1*prec_sub1
Egger_sub1 <- MCMCglmm(zes_sub1~prec_sub1,family="gaussian", data=data.frame(ES=es_sub1,Prec=prec_sub1),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub1)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)    0.6058  -3.5022   4.4985     2236 0.758 # no publ. bias
#prec_sub1     -0.3294  -2.5375   1.7972     2212 0.760
#plot(Egger_sub1)
save(Egger_sub1,file="data/Egger_sub1.RData")
#load("data/Egger_sub1.RData")

###### Cal.Plus.Anx (sub2)
df <- Z_data_list[[3]]
load("runs/M3.1_sub2.Rdata") #load best full model results
model_sub2 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub2 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub2 <- df$H.d - predict(model_sub2)
zes_sub2 <- es_sub2*prec_sub2
Egger_sub2 <- MCMCglmm(zes_sub2~prec_sub2,family="gaussian", data=data.frame(ES=es_sub2,Prec=prec_sub2),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub2)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)    4.8189   0.2850   8.9794     3000 0.0313 * # publ. bias
#prec_sub2     -2.6052  -4.8970  -0.1954     3000 0.0327 *
#plot(Egger_sub2)
save(Egger_sub2,file="data/Egger_sub2.RData")
#load("data/Egger_sub2.RData")

###### Cal.Neg.Act (sub3)
df <- Z_data_list[[4]]
load("runs/M3.3_sub3.Rdata") #load best full model results
model_sub3 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub3 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub3 <- df$H.d - predict(model_sub3)
zes_sub3 <- es_sub3*prec_sub3
Egger_sub3 <- MCMCglmm(zes_sub3~prec_sub3,family="gaussian", data=data.frame(ES=es_sub3,Prec=prec_sub3),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub3)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)   -1.7843  -4.3830   0.6598     3000 0.174 # no publ. bias
#prec_sub3      0.8972  -0.3522   2.1279     3000 0.153
#plot(Egger_sub3)
save(Egger_sub3,file="data/Egger_sub3.RData")
#load("data/Egger_sub3.RData")

###### Cal.Neg.Exp (sub4)
df <- Z_data_list[[5]]
load("runs/M3.3_sub4.Rdata") #load best full model results
model_sub4 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub4 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub4 <- df$H.d - predict(model_sub4)
zes_sub4 <- es_sub4*prec_sub4
Egger_sub4 <- MCMCglmm(zes_sub4~prec_sub4,family="gaussian", data=data.frame(ES=es_sub4,Prec=prec_sub4),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub4)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)   -1.0397  -4.3208   2.3131     3000 0.489 # no publ. bias
#prec_sub4      0.1675  -1.2433   1.5070     3000 0.789
#plot(Egger_sub4)
save(Egger_sub4,file="data/Egger_sub4.RData")
#load("data/Egger_sub4.RData")

###### Cal.Neg.Anx (sub5)
df <- Z_data_list[[6]]
load("runs/M3.3_sub5.Rdata") #load best full model results
model_sub5 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub5 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub5 <- df$H.d - predict(model_sub5)
zes_sub5 <- es_sub5*prec_sub5
Egger_sub5 <- MCMCglmm(zes_sub5~prec_sub5,family="gaussian", data=data.frame(ES=es_sub5,Prec=prec_sub5),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub5)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)   -0.2849  -6.6639   5.9132     3000 0.933 # no publ. bias
#prec_sub5      0.3924  -2.3701   2.8661     3000 0.769
#plot(Egger_sub5)
save(Egger_sub5,file="data/Egger_sub5.RData")
#load("data/Egger_sub5.RData")

###### Pro.Neg.Act (sub6)
df <- Z_data_list[[7]]
load("runs/M3.2_sub6.Rdata") #load best full model results
model_sub6 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub6 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub6 <- df$H.d - predict(model_sub6)
zes_sub6 <- es_sub6*prec_sub6
Egger_sub6 <- MCMCglmm(zes_sub6~prec_sub6,family="gaussian", data=data.frame(ES=es_sub6,Prec=prec_sub6),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub6)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)  -0.06269 -0.62313  0.52058     3000 0.815 # no publ. bias
#prec_sub6     0.02096 -0.17446  0.22386     3000 0.842
#plot(Egger_sub6)
save(Egger_sub6,file="data/Egger_sub6.RData")
#load("data/Egger_sub6.RData")

###### Pro.Neg.Exp (sub7)
df <- Z_data_list[[8]]
load("runs/M3.2_sub7.Rdata") #load best full model results
model_sub7 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub7 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub7 <- df$H.d - predict(model_sub7)
zes_sub7 <- es_sub7*prec_sub7
Egger_sub7 <- MCMCglmm(zes_sub7~prec_sub7,family="gaussian", data=data.frame(ES=es_sub7,Prec=prec_sub7),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub7)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)   -0.2835  -1.1477   0.4817     3000 0.498 # no publ. bias
#prec_sub7      0.1138  -0.1452   0.4031     2950 0.427
#plot(Egger_sub7)
save(Egger_sub7,file="data/Egger_sub7.RData")
#load("data/Egger_sub7.RData")

###### Pro.Neg..Anx (sub8)
df <- Z_data_list[[9]]
load("runs/M3.2_sub8.Rdata") #load best full model results
model_sub8 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub8 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub8 <- df$H.d - predict(model_sub8)
zes_sub8 <- es_sub8*prec_sub8
Egger_sub8 <- MCMCglmm(zes_sub8~prec_sub8,family="gaussian", data=data.frame(ES=es_sub8,Prec=prec_sub8),verbose=TRUE,nitt=100000,thin=25,burnin=25000)
summary(Egger_sub8)
#            post.mean l-95% CI u-95% CI eff.samp pMCMC
#(Intercept)  -1.14085 -2.68737  0.15045     3008 0.1140 # no publ. bias
#prec_sub8     0.49788 -0.05994  1.09218     3000 0.0833
#plot(Egger_sub8)
save(Egger_sub8,file="data/Egger_sub8.RData")
#load("data/Egger_sub8.RData")
```

3. funnel plots on raw data 
--------------------------------------------------------------------------------
Raw effect size estimates (difference between prenatally manipulated and control offspring groups; Hedge’s d) plotted against their precision (1/SE)
Overall postrior (meta-analytic) means are shown as solid lines. 
Zero effect size is shown as dashed line.

```{r funnel raw, echo=FALSE, message=FALSE}

#pdf(file="plots/Rplot_funnel_raw.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,1,1.75),oma=c(0,1,0,0))

###### Cal.Plus.Act (sub1)
df <- Z_data_list[[1]]
meta_sub1 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub1, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.238, col="red", lwd=1, lty=1)
title(main = "Cal.Plus.Act (sub1)", adj=0.5)

###### Cal.Plus.Exp
df <- Z_data_list[[2]]
meta_sub2 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub2, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2)
abline(v=0, lwd=1, lty=2)
abline(v=1.129, col="red", lwd=1, lty=1)
title(main = "Cal.Plus.Exp ()", adj=0.5)

###### Cal.Plus.Anx (sub2)
df <- Z_data_list[[3]]
meta_sub2 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub2, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.173, col="red", lwd=1, lty=1)
title(main = "Cal.Plus.Anx (sub2)", adj=0.5)

###### Cal.Neg.Act (sub3)
df <- Z_data_list[[4]]
meta_sub3 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub3, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.705, col="red", lwd=1, lty=1)
title(main = "Cal.Neg.Act (sub3)", adj=0.5)

###### Cal.Neg.Exp (sub4)
df <- Z_data_list[[5]]
meta_sub4 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub4, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.382, col="red", lwd=1, lty=1)
title(main = "Cal.Neg.Exp (sub4)", adj=0.5)

###### Cal.Neg.Anx (sub5)
df <- Z_data_list[[6]]
meta_sub5 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub5, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.338, col="red", lwd=1, lty=1)
title(main = "Cal.Neg.Anx (sub5)", adj=0.5)

###### Pro.Neg.Act (sub6)
df <- Z_data_list[[7]]
meta_sub6 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub6, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=-0.067, col="red", lwd=1, lty=1)
title(main = "Pro.Neg.Act (sub6)", adj=0.5)

###### Pro.Neg.Exp (sub7)
df <- Z_data_list[[8]]
meta_sub7 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub7, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.007, col="red", lwd=1, lty=1)
title(main = "Pro.Neg.Exp (sub7)", adj=0.5)

###### Pro.Neg.Exp (sub8)
df <- Z_data_list[[9]]
meta_sub8 <- metagen(df$H.d, sqrt(df$H.d_Var_combined))
funnel.meta(meta_sub8, yaxis = "invse", xlab="Hedge's d", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,6), pch=16, level=NULL, comb.fixed=FALSE, comb.random=FALSE, cex=1.2) # contour=c(0.95), col.contour=("lightgrey")
abline(v=0, lwd=1, lty=2)
abline(v=0.074, col="red", lwd=1, lty=1)
title(main = "Pro.Neg.Anx (sub8)", adj=0.5)

#dev.off()
```

4. funnel plots on residuals from full models 
--------------------------------------------------------------------------------
Residual effect sizes from the full model (adjusted for moderators) plotted against their precision (1/SE)
Zero effect size is shown as dashed line.

```{r funnel res, echo=FALSE, message=FALSE}
#pdf(file="plots/Rplot_funnel_residuals.pdf",width=8,height=7,family="sans",pointsize=10)

par(mfcol=c(3,3),mar=c(4,4,1,1.75),oma=c(0,1,0,0))

###### Cal.Plus.Act (sub1)
df <- Z_data_list[[1]]
load("runs/M3.1_sub1.Rdata") #load best full model results
model_sub1 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub1 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub1 <- df$H.d - predict(model_sub1)
zes_sub1 <- es_sub1*prec_sub1
plot(es_sub1,prec_sub1, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Plus.Act (sub1)", adj=0.5)

###### Cal.Plus.Exp (moments method! use (x - mu) as residuals)
df <- Z_data_list[[2]]
prec_moment <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_moment <- df$H.d - 1.129344
zes_moment <- es_moment*prec_moment
plot(es_moment, prec_moment, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Plus.Exp ()", adj=0.5)

###### Cal.Plus.Anx (sub2)
df <- Z_data_list[[3]]
load("runs/M3.1_sub2.Rdata") #load best full model results
model_sub2 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub2 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub2 <- df$H.d - predict(model_sub2)
zes_sub2 <- es_sub2*prec_sub2
plot(es_sub2,prec_sub2, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Plus.Anx (sub2)", adj=0.5)

###### Cal.Neg.Act (sub3)
df <- Z_data_list[[4]]
load("runs/M3.3_sub3.Rdata") #load best full model results
model_sub3 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub3 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub3 <- df$H.d - predict(model_sub3)
zes_sub3 <- es_sub3*prec_sub3
plot(es_sub3,prec_sub3, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Neg.Act (sub3)", adj=0.5)

###### Cal.Neg.Exp (sub4)
df <- Z_data_list[[5]]
load("runs/M3.3_sub4.Rdata") #load best full model results
model_sub4 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub4 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub4 <- df$H.d - predict(model_sub4)
zes_sub4 <- es_sub4*prec_sub4
plot(es_sub4,prec_sub4, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Neg.Exp (sub4)", adj=0.5)

###### Cal.Neg.Anx (sub5)
df <- Z_data_list[[6]]
load("runs/M3.3_sub5.Rdata") #load best full model results
model_sub5 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub5 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub5 <- df$H.d - predict(model_sub5)
zes_sub5 <- es_sub5*prec_sub5
plot(es_sub5,prec_sub5, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Cal.Neg.Anx (sub5)", adj=0.5)

###### Pro.Neg.Act (sub6)
df <- Z_data_list[[7]]
load("runs/M3.2_sub6.Rdata") #load best full model results
model_sub6 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub6 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub6 <- df$H.d - predict(model_sub6)
zes_sub6 <- es_sub6*prec_sub6
plot(es_sub6,prec_sub6, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Pro.Neg.Act (sub6)", adj=0.5)

###### Pro.Neg.Exp (sub7)
df <- Z_data_list[[8]]
load("runs/M3.2_sub7.Rdata") #load best full model results
model_sub7 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub7 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub7 <- df$H.d - predict(model_sub7)
zes_sub7 <- es_sub7*prec_sub7
plot(es_sub7,prec_sub7, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Pro.Neg.Exp (sub7)", adj=0.5)

###### Pro.Neg.Exp (sub8)
df <- Z_data_list[[9]]
load("runs/M3.2_sub8.Rdata") #load best full model results
model_sub8 <- model
#next 2 lines are modified for the models controlling for shared control groups
prec_sub8 <- 1/sqrt(df$H.d_Var_combined) # Precision = 1/sqrt(V)
es_sub8 <- df$H.d - predict(model_sub8)
zes_sub8 <- es_sub8*prec_sub8
plot(es_sub8,prec_sub8, xlab="Egger's regressed effect sizes", ylab="Precision (1/SE)", xlim=c(-5,5), ylim=c(0,8), pch=16, cex=1.2)
abline(v=0, lwd=1, lty=2)
title(main = "Pro.Neg.Exp (sub8)", adj=0.5)

#dev.off()
```


4. forest plots 
--------------------------------------------------------------------------------
Zero effect size is shown as dashed line.


```{r forest plot}
varnames_full <- rev(c("Male mean","Mixed-sex mean", "Female mean","Dam dietary manipulation level",
                "Dam dietary manipulation start time","Offspring age at testing","Dam dietary manipulation end time","Meta-analytic (overall) mean"))
varnames_models <- rev(c("factor(sex)m","factor(sex)both","factor(sex)f","Z_nom_manip_val","Z_dam_diet_start_dPC","Z_response_age_dPP","Z_dam_diet_end_dPC","intercept"))
varnames <- as.data.frame(cbind(varnames_models, varnames_full))
#tiff(file="plots/Rplot_forest_plot_v1.tif",width=6.30708661,height=4,res=400,units="in",pointsize=9)
#
pdf(file="plots/Rplot_forest_plot_v1.pdf",width=15,height=10,pointsize=16,family="sans",encoding="CP1250")

par(mfcol=c(3,3),mar=c(4,14,1,1.75),oma=c(0,1,0,0))

###### Cal.Plus.Act (sub1)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalPlusAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 3) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalPlusAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Cal.Plus.Act (sub1)", adj = 0.5, cex=1.2)


###### Cal.Plus.Anx (moment method - only overall result available)
data <- read.csv("data/Cal.Plus.Exp.csv")
weights <- 1/data$SE.d^2
effects <- data$H.d
mu <- sum(effects * weights) / sum(weights)
var <- 1 / sum(weights)
t <- mu / sqrt(var)
CI <- sqrt(var) * qt(0.05/2, df=1)
#mu+CI # -3.619431
#mu    #  1.129344
#mu-CI #  5.878119
#plot mean
plot(mu,1,ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
# add segments
segments(mu+CI,1,mu-CI,1,lwd=1.25)
#add labels
for (i in 1:length(varnames$varnames_full)){   mtext(varnames$varnames_full[i],2,0,at=i,las=2,cex=.7) }
abline(v=0,lty=3)
title(main = "Cal.Plus.Exp (moment)", adj = 0.5, cex=1.2)


###### Cal.Plus.Anx (sub2)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalPlusAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 5) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalPlusAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Cal.Plus.Anx (sub2)", adj = 0.5, cex=1.2)


###### Cal.Neg.Act (sub3)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 5) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Cal.Neg.Act (sub3)", adj = 0.5, cex=1.2)

stars<-c("*","","","","","","","")
for (i in 1:length(stars)){
  mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1)
}


###### Cal.Neg.Exp (sub4)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegExp_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegExp_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Cal.Neg.Exp (sub4)", adj = 0.5, cex=1.2)

stars<-c("","","","","*","","","")
for (i in 1:length(stars)){
  mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1)
}


###### Cal.Neg.Anx (sub5)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_CalNegAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 4) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_CalNegAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Cal.Neg.Anx (sub5)", adj = 0.5, cex=1.2)



###### Pro.Neg.Act (sub6)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegAct_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegAct_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Pro.Neg.Act (sub6)", adj = 0.5, cex=1.2)


###### Pro.Neg.Exp (sub7)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegExp_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegExp_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Pro.Neg.Exp (sub7)", adj = 0.5, cex=1.2)


###### Pro.Neg.Anx (sub8)
### use the tables of extracted runs results, rather than the original runs!
# get full model results:
table <- read.csv("tables/results_table_ProNegAnx_M3.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 6) # adjust nrows according to the number of moderatorsused !
# get intercept model results:
null <- read.csv("tables/results_table_ProNegAnx_M1.csv", header=FALSE, skip = 4, col.names = c("Moderator","Mode","Mean","SD","Lower","Upper"), nrows = 1) #just read the intercept (overall mean)
# just get the first row out (the intercept) and attach to the table with full model results:
table1 <- rbind(table, null[1,])
table2 <- merge(varnames, table1, by.x = "varnames_models", by.y = "Moderator", incomparables = NA, all = TRUE)
table2 <- table2[c(4,5,8,6,7,2,1,3),] #re-order
#table2
#set shape and size of point estimates 
Shape <- c(18,rep(16,dim(table2)[1]))
Size <- c(1.5,rep(1.2,dim(table2)[1]))
#plot point estimates
plot(table2$Mean,1:dim(table2)[1],ylab=NA,yaxt="n",bty="n",xlim=c(-5,5),ylim=c(0.25,dim(table2)[1]+.5),xlab="Hedge's d",pch=Shape,cex=Size,cex.axis=.9)
#add labels
for (i in 1:length(table2$varnames_full)){  mtext(table2$varnames_full[i],2,0,at=i,las=2,cex=.7) }
# add segments
for (i in 1:length(table2$Mean)){  segments(table2$Lower[i],i,table2$Upper[i],i,lwd=1.25)  }
abline(v=0,lty=3)
title(main = "Pro.Neg.Anx (sub8)", adj = 0.5, cex=1.2)

stars<-c("","","","","","","","*")
for (i in 1:length(stars)){
  mtext(stars[i],2,-1,at=i-0.2,las=2,cex=1)
}

dev.off()
```

